Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-18 tex/paper1/paper1.tex
edits to the paper

This derivation of a \PL\ \PS\ shares many similar features
with the nanoflare model of {\it energy} deposition in the solar
atmosphere. In the nanoflare model,

However, inferring the properties of energy deposition events from the
observed emission \PL\ \PS\ depends strongly on three factors
that influence the observation.  Firstly, the distribution of events
along the line of sight and their temporal dependence (expressed
through the parameters $\alpha_{E}$ and $\gamma$ in Equation
\ref{eqn:energydistrib}) have strong effects on the observed \Fps.
Secondly, the energy radiated as a function of the energy deposited in
each event and the existing plasma properties must be consistently
modeled.  This is required to understand how much radiation at each
wavelength is emitted from the plasma.  This is a complex task to do
correctly, and there is much work ....

@@

>>>>

This derivation of a \PL\ \PS\ shares many similar features with the
nanoflare model of {\it energy} deposition in the solar atmosphere. In
the nanoflare model advanced by \cite{1988ApJ...330..474P}, large
numbers of small magnetic reconnection events convert the energy in
the magnetic field into energy that heats the corona.  Nanoflares are
hypothesized to be small ($10^{24}-10^{27}$ ergs) yet ubiquitous in
the corona.  \cite{2013ApJ...771...21W} and \cite{2013ApJ...770L...1T}
analyzing narrowband 193\AA\ images taken by the Hi-C instrument on
board a sounding rocket demonstrate the heating of small scale coronal
structures that appear to be consistent with scenarios of nanoflare
heating due to reconnecting magnetic loops.  However, the nanoflare
occurence rate, or their energy distribution for the entire solar
atmosphere is as yet unknown.

Any modeling or theoretical effort to infer the occurence rate and
energy distribution of energy deposition events from the observed
emission \PL\ \PS\ depends strongly on three factors that influence
the observation.  Firstly, it is known that many loops lie along the
line-of-sight in the corona \citep{???}.  Each of these may have
different emission measures, temperatures and densities.  The location
of energy deposition may not be the same for each loop \citep{???}.
This implies that attempts to work back from the observed emission to
the underlying energy deposition must properly account for these
line-of-sight effects.

Secondly, since each loop is different, and the reaction of the
coronal plasma to an energy deposition event is a highly nonlinear
function of the coronal conditions it occurs in,

  It is known that

Secondly, the energy radiated as a function of the energy deposited in
each event and the existing plasma properties must be consistently
modeled.  This is required to understand how much radiation at each
wavelength is emitted from the plasma.  This is a complex task to do
correctly, and there is much work ....

@@

These three factors will all have an effect on the inferred properties
of the energy deposition rate.  The observed \PL\ \PS\ here, coupled
with the emission event hypothesis and a modeling effort that takes
account of the factors above, offers a new way to constrain the energy
deposition rate in the solar corona.  Under the hypothesis, the energy
deposition rate can be explored through the distribution of the number
of events along the line-of-sight and their temporal dependence,
expressed through the parameters $\alpha_{E}$ and $\gamma$ in Equation
\ref{eqn:energydistrib}.
